Get utilization standards and piece size by FMU and township

### 2021-09-10 analysis/get_util_piece_size.Rmd
thing

---
title: "Get utilization standards and piece size by FMU"
author:
- Glen W Armstrong^[Department of Renewable Resources, University of Alberta]
date: "2021-09-10"
output:
  html_document:
    df_print: paged
  word_document:
  pdf_document:
    number_sections: yes
    latex_engine: xelatex
    keep_tex: yes
bibliography: historicalResidueSupply.bib
---

@@

```{r read data files, echo=FALSE}
util_std <- read.csv(file = '../data/util_std.csv')
piece_size <- read.csv(file = '../data/piece_size.csv')
fmu_twp <- read.csv(file ='../data/FMU_TWP.csv')
head(util_std)
head(piece_size)
head(fmu_twp)
util_piece <-full_join(util_std,piece_size,by=c("FMU","CD"))
util_piece_fmu_twp <- full_join(util_piece,fmu_twp,by="FMU")
util_piece_fmu_twp$piece_size <- 1/util_piece_fmu_twp$logspm3
head(util_piece_fmu_twp)

>>>>

---
title: "Get utilization standards and piece size by FMU and township"
author:
- Glen W Armstrong^[Department of Renewable Resources, University of Alberta]
date: "2021-09-10"
output:
  html_document:
    df_print: paged
  word_document:
  pdf_document:
    number_sections: yes
    latex_engine: xelatex
    keep_tex: yes
bibliography: historicalResidueSupply.bib
---

@@

```{r read data files, echo=FALSE}
util_std <- read.csv(file = '../data/util_std.csv')
piece_size <- read.csv(file = '../data/piece_size.csv')
fmu_twp <- read.csv(file ='../data/FMU_TWP.csv')
head(util_std)
head(piece_size)
head(fmu_twp)
util_piece <-full_join(util_std,piece_size,by=c("FMU","CD"))
util_piece_fmu_twp <- full_join(util_piece,fmu_twp,by="FMU")
util_piece_fmu_twp$piece_size <- 1/util_piece_fmu_twp$logspm3
util_piece_fmu_twp
